Refinements for open automata

### 2023-03-09 2021-Refinement/paper/refinementarticleV2.tex
point dsicute ce matin

Moreover, we have  for any transition $t_1 $ in $A_1$ relying $s_3$ and $s^{\prime}_1$ the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

From the two previous formula, we get:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
		\end{array}}   
\end{multline*}

@@

Thus, we get:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
R\mpar{s_2, s_{3}} \wedge g_{12} \land \reach{A_{12}}\mpar{s_{12}} \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
\wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
		\end{array}}   
\end{multline*}

Because of the independence of the substitution domains, we simplify and get the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}}   
\end{multline*}

\paragraph{Second case: Only the encompassing automaton performs a transition.}
  $t_{12}$ is obtained by the transition 
$\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
\]
As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
 with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3x}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]

@@

For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$, $g_{13x}  \Leftrightarrow g^2_1$, $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} =  \alpha^2_1$.  Furthermore, we have the actions of the holes in $J_{13}$ coincide by the composition, $\beta_{13j}$ and $\beta_{23xj}$  are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.

\TODO{D'apres l'hypothese de depart, la formule (*) nous obtenons une formule sous cette forme: $R\mpar{s_2, s_3} \wedge g_2 \implies R\mpar{s'_2, s'_{3x}}$  l'idee est de faire disparaitre g2. On a la formule suivante:}

According to the relation between $A_2$ and $A_3$ open automata,  for all $\mpar{s_2, s_{3}} \in S_2\times S_3$  we have:
\begin{multline*}
 V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \wedge \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} )\implies \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}  )
\end{multline*}

\TODO{La conjonction des deux donne $False \implies R\mpar{s'_2, s'_{3x}}$ qui true???}

>>>>

Moreover, we have  for any transition $t_1 $ in $A_1$ relying $s_3$ and $s^{\prime}_1$ the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

From the two previous formula, we get:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
		\end{array}}   
\end{multline*}

@@

Thus, we get:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
R\mpar{s_2, s_{3}} \wedge g_{12} \land \reach{A_{12}}\mpar{s_{12}} \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
\wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
		\end{array}}   
\end{multline*}

Because of the independence of the substitution domains, we simplify and get the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}}   
\end{multline*}

\paragraph{Second case: Only the encompassing automaton performs a transition.}
  $t_{12}$ is obtained by the transition 
$\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
\]
As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
 with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]

@@

\medskip
\TODO{To check form this point}

We have for all $\mpar{s_{2}, s_{3}} \in S_{2} \times S_{3}$ such that $\reach{A_{12}}(s_{12})$ is satisfiable:
\begin{align*}
 R\mpar{s_{2}, s_{3}} &\implies  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \\
 & \implies
R' \mpar{s_{12}, s_{13}}
\end{align*}

Since in this case the state $s'_{12}$ is the same as $s_{12}$ and $s'_{13x}$ is the same as $s_{13}$, we get:
\begin{align*}
 R\mpar{s_{2}, s_{3}}  & \implies
R' \mpar{s_{12}, s_{13}}\\
& \implies
R' \mpar{s'_{12}, s'_{13x}}
\end{align*}
Furthermore for this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12}$ is the same as $ g^1_1$, $g_{13x}$    as $g^2_1$, $\alpha_{12}$ as $\alpha^1_1$ and $\alpha_{23x}$ as  $\alpha^2_1$.  Similarly, 
$\beta_{13j}$ and $\beta_{23xj}$ are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.\\

Moreover, we have  for any transition $t_1$ in $A_1$ that is used to build $t_{12}$ and $t_{13x}$ the following:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
\end{multline*}

From the above we can deduce the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}}   
\end{multline*}
